Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-09 edubots_surveys.Rnw
Clarify the survey to which we refer to
Addressing another comment

Our intention from the beginning was to try to gather a sufficient amount of
responses in all sectors, as well as cover different sectors of higher
education. In doing so, an online survey was administered (i.e., Google Form),
in Spanish, which was intended to be answered in a very short amount of
time. Initially, our intention was to mirror the questions used in
\cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
to create a second survey. The survey items focused on the use of messaging apps
in the teaching practice, the type of chatbot use cases that teachers consider
useful to be used in their teaching, and the type of interactions that teachers
prefer to have with their students while using messaging apps in their teaching.

>>>>

Our intention from the beginning was to try to gather a sufficient amount of
responses in all sectors, as well as cover different sectors of higher
education. In doing so, an online survey was administered (i.e., Google Form),
in Spanish, which was intended to be answered in a very short amount of
time. Initially, our intention was to mirror the questions used in
\cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
to create a second survey. The new survey items focused on the use of messaging apps
in the teaching practice, the type of chatbot use cases that teachers consider
useful to be used in their teaching, and the type of interactions that teachers
prefer to have with their students while using messaging apps in their teaching.
